Group 5 Report

### 2022-08-02 Report/Group 5 report.Rmd
Fixing XML.

At this stage, we wanted to explore alternatives to analyzing PDF
documents. We discussed how to do so, and concluded that we had three
options: 
- Financial statements in yearly report PDF documents. 
- Webscrape Proff.no for financial statements. 
- Webscrape the Brønnøysund registry.

@@

We started to look at workarounds for this problem. It would still be
possible to download Proff.no HTML websites manually for each
organization. And, we attempted to request a temporary access to the
Brønnøysund registry's XML documents. <!-- # Ikke Brønnøysund XML -- de har API. Vi fikk en XML-dump fra SSB, men det er ikke noe OPX kan bruke.-->

>>>>

At this stage, we wanted to explore alternatives to analyzing PDF
documents. We discussed how to do so, and concluded that we had three
options:

- Financial statements in annual report PDF documents. 
- Webscrape Proff.no for financial statements. 
- Webscrape the Brønnøysund registry.

@@

We started to look at workarounds for this problem. It would still be
possible to download Proff.no HTML websites manually for each
organization. We did receive some XML files from Statistics Norway, but using these is ultimately not a viable solution for OPX.
